\documentclass{article}
\usepackage{amsmath}
\begin{document}

Homework 1$\newline$
Will Boland$\newline$
01/10/2019$\newline$


Question 1$\newline$

A) not a proposition$\newline$
B) proposition: false. The lottery, while usually requires a purchased ticket, could be won by having a special sort of promotion not requiring purchase.$\newline$
C) not a proposition $\newline$
D) not a proposition$\newline$
E) not a proposition$\newline$
F) proposition: false. We can measure the height of humans and we have demonstrated that there exist some that are greater than six feet tall.$\newline$
G) proposition: false. This is false because questions are not propositions due to the fact they aren’t stating an opinion but inquiring about a topic.$\newline$
H) not a proposition$\newline$
I) proposition: false. Six multiplied by nine is fifty four.$\newline$
J) not a proposition$\newline$
K) proposition: true. It is true because 1 + 1 = 2, which makes the greater than or equal to equality true as well.$\newline$
L) proposition: false. 1 + 1 is equal to 2, and not 5.$\newline$
$\newline$

Question 2$\newline$

A) I am allergic to penicillin; therefore, taking penicillin may cause a rash. (a note I wrote during a Philmont trip in 2016, for medical records)$\newline$
B) I don’t know if I left my keys at home. (My mom) - She was looking for her keys and couldn’t find them.$\newline$

$\newline$
Question 3$\newline$

A) R $\wedge$ $\neg$Q$\newline$
B) Q $\rightarrow$ R$\newline$
C) R $\rightarrow$ Q$\newline$
D) R $\leftrightarrow$ Q$\newline$
E) R $\leftrightarrow$ (Q $\lor$ P)$\newline$
F) P $\wedge$ Q $\wedge$ R$\newline$
G) R $\rightarrow$ P$\newline$
H) R $\rightarrow$ P$\newline$
I) ((P $\wedge$ $\neg$Q)) $\wedge$ R$\newline$
$\newline$

Question 4$\newline$

A) R: The suspect wore gloves. P: He didn’t touch it$\newline$
R $\oplus$ $\neg$P$\newline$$\newline$
B) R: Eat my tie. P: Cubs win the World Series.$\newline$
P $\rightarrow$ R$\newline$$\newline$
C) R: it smelled funny. P: Ate it.$\newline$
R $\wedge$ P$\newline$$\newline$
D) R: The people gave up their arms. P: Tyrant resigns. Q: Get money back money back.$\newline$
R $\rightarrow$ (P $\wedge$ Q)$\newline$$\newline$
E) R: Prizes awarded. P: sufficient number of entries received.$\newline$
P $\rightarrow$ R$\newline$$\newline$
F )R: absence of antibodies in body. P: are susceptible to infection.$\newline$
R $\rightarrow$ $\neg$P$\newline$$\newline$
G) R: Participants were timed on this task. P: finished in less than 8 minutes.$\newline$
$\neg$R $\wedge$ P$\newline$$\newline$
H) R: Holds black ink cartridge. P: Holds color cartridge.$\newline$
R $\oplus$ P$\newline$$\newline$
I) R: person has a real desire to want to change. P: Puts forth real effort to make those changes. X: Changes come about.$\newline$
(R $\wedge$ P) $\rightarrow$ X$\newline$$\newline$
J) R: Lyapunov function exists. P: the system is stable.$\newline$
R $\leftrightarrow$ P$\newline$$\newline$
K) R: Regulation applies. P: both houses vote to impose regulation.$\newline$
$\neg$P $\lor$ $\neg$R$\newline$$\newline$

$\newline$
Question 5$\newline$
A) I entered the lottery or I won the jackpot.$\newline$
IB) f I won the jackpot then I entered the lottery.$\newline$
C) I won the jackpot if and only if I entered the lottery.$\newline$
D) If I didn’t enter the lottery then I didn’t win the jackpot.$\newline$
E) I did not enter the lottery and I did not win the jackpot.$\newline$
F) I did not enter the lottery, or I entered the lottery and won the jackpot.$\newline$

$\newline$
Question 6$\newline$
A) I would first prove that either p is true or q is true, or that both p and q is true.$\newline$
B) I would first prove that p is true then prove that q is also true, or I could simply prove that p is true and that q is not true, which would leave the only conditional claim that is false. From that, we know all other possibilities lead to true.$\newline$
C) I would prove that not p is true and demonstrate that p is false, or vice versa.$\newline$
D) I would prove that p is true and q is true, or that p is false and q is false, and demonstrate that all other condition for p and q is not true.$\newline$
E) I would prove that p is true and q is false, or that p is false and q is true, or that p is false and q is false.$\newline$

$\newline$
Question 7 (Bonus)$\newline$

The TV was on, and the TV was plugged in.
\end{document}